%-------------------------
% Saif M. Hakeam Resume
% Matches original PDF layout exactly
%-------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[normalem]{ulem}
\usepackage[hidelinks]{hyperref}
\hypersetup{
    pdfborder={0 0 0},
    colorlinks=false
}

% Standard Google/MS Docs blue color
\definecolor{docblue}{RGB}{17, 85, 204}

% Custom command for blue text with blue underline (using ulem for guaranteed underline)
\newcommand{\myhref}[2]{\href{#1}{\color{docblue}\uline{#2}}}

\usepackage[english]{babel}
\usepackage{tabularx}

% Page style - no headers/footers
\pagestyle{empty}

% Adjust margins to match original
\setlength{\oddsidemargin}{-0.5in}
\setlength{\evensidemargin}{-0.5in}
\setlength{\textwidth}{7.0in}
\setlength{\topmargin}{-0.75in}
\setlength{\textheight}{10.7in}
\setlength{\headheight}{0pt}
\setlength{\headsep}{0pt}
\setlength{\footskip}{10pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\parindent}{0pt}

% Use Sans Serif font globally
\renewcommand{\familydefault}{\sfdefault}

% Section formatting - cleaner and thinner rule
\renewcommand{\section}[1]{
  \vspace{5pt}
  {\large\bfseries #1}
  \vspace{2pt}
  \par\noindent\rule{\textwidth}{0.5pt}
  \vspace{2pt}
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r}
  \myhref{mailto:saif.hakeam97@gmail.com}{saif.hakeam97@gmail.com} & \textbf{\Huge \scshape Saif M. Hakeam} & \myhref{https://github.com/saifhakeam}{GitHub} \\
  +(971) 56 322 5389 & & \myhref{https://linkedin.com/in/saif-hakeam}{LinkedIn} \\
  Abu Dhabi, UAE & & \\
\end{tabular*}

%-----------SUMMARY-----------
\section{Summary}

\textbf{Software Engineer} with \textbf{4 years} of experience working in the fields of \textbf{Security, FinTech, Machine Learning}, mobile \textbf{SDKs \& cross-platform} plugins. I have a proven track record of building and integrating \textbf{mission-critical} SDKs used by \textbf{Banks. 3x AWS} certified with strong \textbf{backend} experience.

%-----------EXPERIENCE-----------
\section{Professional Experience}

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{Software Engineer - Mobile SDK} & Aug 2022 - Present \\
  \textit{\myhref{https://www.callsign.com}{Callsign Technologies}} & \textit{Abu Dhabi, UAE} \\
\end{tabular*}

\vspace{1pt}
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parsep}{0pt}
  \setlength{\topsep}{0pt}
  \item Worked in a team of 3 to build \textbf{Cordova plugin} for the \textbf{Callsign SDK}, enabling a major Irish credit union to migrate to a new \textbf{SaaS} platform and reduce operational \textbf{costs by over \$250,000 annually}.
  \item Led the \textbf{development and maintenance} of \textbf{Callsign SDK} packages for \textbf{React-Native} and \textbf{Flutter}, used by two major banks in the Gulf Region serving over \textbf{500,000 users}.
  \item Delivered over \textbf{10 successful releases} of \textbf{Cordova, React Native, and Flutter plugins}, while providing comprehensive support for client integration, QA, and UAT.
  \item Built an end-to-end \textbf{CI/CD} for \textbf{Cordova, React-Native, and Flutter} applications, reducing the release cycle from \textbf{a week to less than a day}.
\end{itemize}

\vspace{2pt}
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{Technical Founder} & Oct 2021 - Jan 2024 \\
  \textit{Injaz} & \textit{Mosul, Iraq} \\
\end{tabular*}

\vspace{1pt}
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parsep}{0pt}
  \setlength{\topsep}{0pt}
  \item Single-handedly built accounting platform managing over \textbf{\$200K annually} for a leading construction contractor.
  \item Scaled system into a \textbf{SaaS}, accommodating multiple companies concurrently due to popular demand.
  \item Implemented admin and user web \textbf{PWAs} using \textbf{Flutter} and built backend using \textbf{Node.JS and Firebase}.
  \item Designed the system with information \textbf{security and integrity} in mind by using \textbf{DDD architecture} and configured both the front and back-end security rules by the \textbf{principle of least privilege}.
  \item Eliminated money mismanagement and fraud of funds by fully transitioning the company to \textbf{paperless accounting}.
  \item Client fully switched to the system after a \textbf{single week of testing} thanks to the reliability and convenience.
\end{itemize}

%-----------EDUCATION-----------
\section{Education}

\noindent
\textbf{AWS Certified Solutions Architect and Developer -- Associate} \myhref{https://www.credly.com/badges/your-architect-badge-id}{Architect} \myhref{https://www.credly.com/badges/your-developer-badge-id}{Developer} \myhref{https://www.credly.com/badges/your-practitioner-badge-id}{Practitioner} \hfill Feb 2025 \\[0pt]
\textbf{The American University of Iraq - Sulaimani (AUIS)} B.S. in IT \hfill Sep 2017 - Jul 2021 \\[0pt]
\textbf{Stanford Online:} Algorithms Design and Analysis Part I \& II \hspace{1em} \myhref{https://coursera.org/verify/your-certificate-id}{Verified Certificate} \hfill Sep 2020 \\[0pt]
\textbf{Stanford Online:} Machine Learning \hspace{1em} \myhref{https://coursera.org/verify/your-certificate-id}{Verified Certificate} \hfill Dec 2020

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\vspace{-2pt}
\noindent
\textbf{Programming Languages:} Experienced in Dart, Python, Java, JavaScript. Familiar with Kotlin, Swift, Objective-C, Go. \\[0pt]
\textbf{Frameworks:} Experienced in Flutter, Android, Gradle, NodeJS, Docker, Fastlane. \\[0pt]
\textbf{Cloud:} Experienced in AWS, Firebase - GCP. \\[0pt]
\textbf{Tools:} Vim, Jira, DexGuard, Linux.

%-------------------------------------------
\end{document}
